Implementing simplified INLA into `aghq`

### 2022-11-04 src/dev_sinla/sinla.Rmd
Add resources
Develop non-empirical Bayes method using modesandhessians

```{r}
h_norm <- function(theta) h$fn(theta) - quad$normalized_posterior$lognormconst
```

@@

@@

>>>>

```{r}
h_norm <- function(theta) h$fn(theta) + quad$normalized_posterior$lognormconst
```

@@

We're going to start by normalising $\tilde p_\text{LA}(\theta, y)$.
Remember that we did this above in the empirical Bayes case, but found that it wasn't strictly necessary.

```{r}
h$he <- function(theta) numDeriv::jacobian(h$gr, theta, method = "Richardson")
quad <- aghq::aghq(ff = h, k = 3, startingvalue = c(0, 0), control = aghq::default_control_tmb())
quad$normalized_posterior$lognormconst
h_norm <- function(theta) h$fn(theta) + quad$normalized_posterior$lognormconst
```

We can get the mode and Hessian of the random effects at each quadrature point as follows:

```{r}
distinctthetas <- quad$normalized_posterior$nodesandweights[, grep('theta', colnames(quad$normalized_posterior$nodesandweights))]
modesandhessians <- distinctthetas
thetanames <- make.unique(names(h$par), sep = "")
colnames(modesandhessians) <- thetanames

modesandhessians$mode <- vector(mode = "list", length = nrow(distinctthetas))
modesandhessians$H <- vector(mode = "list", length = nrow(distinctthetas))

for(i in 1:nrow(distinctthetas)) {
  theta <- as.numeric(modesandhessians[i, thetanames])
  h$fn(theta)
  mm <- h$env$last.par
  modesandhessians[i, "mode"] <- list(list(mm[h$env$random]))
  H <- h$env$spHess(mm, random = TRUE)
  H <- rlang::duplicate(H)
  modesandhessians[i, "H"] <- list(list(H))
}

modesandhessians$weights <- quad$normalized_posterior$nodesandweights$weights
```

Now we want to evaluate
$$
\tilde p(x_i \, | \, y) &= \sum_z \tilde p_\text{G}(x_i \, | \, \theta(z), y) \tilde p_\text{LA}(\theta(z) \, | \, y) w_k(z).
$$
To start with, let's evaluate this for the first value of $z$ (actually I don't really know what $z$ runs over, but this is just the first weight):

```{r}
x_test_value <- 0

z <- 1
i <- 1

#' This is the weight, w_k(z)
modesandhessians$weights[z]

#' This is the normalised Laplace approximation to log(p(theta | y))
theta <- as.numeric(modesandhessians[z, thetanames])
- h_norm(theta)

#' This is the normalised Gaussian approximation to log(p(x_i | theta, y))
#' Let's say that we're doing i = 1 (corresponding to x_i)
mean_i <- as.numeric(modesandhessians$mode[[z]][i])
Sigma <- solve(modesandhessians$H[[z]])
sd_i <- as.numeric(sqrt(Sigma[i, i]))

dnorm(x_test_value, mean = mean_i, sd = sd_i, log = TRUE)

#' So the value we would compute, on the log scale, is
dnorm(x_test_value, mean = mean_i, sd = sd_i, log = TRUE) + (- h_norm(theta)) + log(modesandhessians$weights[z])
```

Remember that we're dealing with the logarithm versions, so let's exp-sum-log for the part inside the sum:
$$
\exp \left( \log\tilde p_\text{G}(x_i \, | \, \theta(z), y) + \log \tilde p_\text{LA}(\theta(z) \, | \, y) + \log w_k(z) \right)
$$

@@

## Resources

* [INLA and other approaches to GAMs](https://www.maths.ed.ac.uk/~swood34/inla-etc.pdf)
* [mgcv::ginla](https://github.com/cran/mgcv/blob/d9fe307c8ed1f8f1ed436c85e4ac415c1febeef4/R/inla.r)
